### 2018-03-26 tex/paper.tex
Restore lost paragraph
Retake snapshots and rewrite progress section

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/screenshot1}
\par\end{centering}
\caption{\label{fig:full-screenshot-demo}Screenshot of the visualisation tool
running the incentivised deposit contract.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.7]{pix/detail1}\caption{\label{fig:detail-of-block}Detail of five interlocked 
blocks.}
\end{figure}

@@

\begin{figure}
\centering{}\includegraphics[scale=0.7]{pix/detail2}\caption{\label{fig:detail-of-interface}Detail of the interface for 
contract
execution simulation.}
\end{figure}

Additionally, to facilitate the introduction of inputs, the tool provides
two different interfaces:
\begin{itemize}
\item The manual interface (see Figure~\ref{fig:detail-of-manual-interface}),
provides a template for each of the four possible types of input:
commits, redeems, payment claims, and choices.
\item The smart interface (see Figure~\ref{fig:detail-of-smart-interface}),
calculates the possible operations that would make sense given the
current inputs, state of the contract, block number, and remaining
contract; and it provides them in a table with most of the parameters
already filled in.
\end{itemize}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.7]{pix/detail3}
\par\end{centering}
\caption{\label{fig:detail-of-manual-interface}Detail of the manual interface.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.7]{pix/detail4}\caption{\label{fig:detail-of-smart-interface}Detail of the smart 
interface.}
\end{figure}

@@

@@

That is, for each contract do there exist sequences of values of \haskellinline{Commit} and \haskellinline{OS} such that stepping the contract with these inputs leads to \haskellinline{Null}? Some relevant points include:
\begin{itemize}
\item For \haskellinline{When}, we need to be able to make \haskellinline{interpretObs st obs os} true. Since there is 
a timeout to \haskellinline{When} then there is no need to impose this condition, as we will progress at timeout if not 
before.
\item As we have put timeouts on to \haskellinline{CommitCash} and \haskellinline{RedeemCC} operations, there are no remaining requirements on these constructs for contract execution to make progress, albeit eventually.
\item We need to check the status of \haskellinline{Observations}: what if an observation is unsatisfiable?
\item There are no constraints on other constructs.
\end{itemize}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/screenshot1}
\par\end{centering}
\caption{\label{fig:full-screenshot-demo}Screenshot of the visualisation tool
simulating the incentivised deposit contract.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.5]{pix/detail1}\caption{\label{fig:detail-of-block}Detail of five interlocked 
blocks.}
\end{figure}

@@

\begin{figure}
\centering{}\includegraphics[scale=0.5]{pix/detail2}\caption{\label{fig:detail-of-interface}Detail of the interface for 
contract
execution simulation.}
\end{figure}

Additionally, to facilitate the introduction of inputs, the tool provides
two different interfaces:
\begin{itemize}
\item The manual interface (see Figure~\ref{fig:detail-of-manual-interface}),
provides a template for each of the four possible types of input:
commits, redeems, payment claims, and choices.
\item The smart interface (see Figure~\ref{fig:detail-of-smart-interface}),
calculates the possible operations that would make sense given the
current inputs, state of the contract, block number, and remaining
contract; and it provides them in a table with most of the parameters
already filled in.
\end{itemize}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{pix/detail3}
\par\end{centering}
\caption{\label{fig:detail-of-manual-interface}Detail of the manual interface.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.5]{pix/detail4}\caption{\label{fig:detail-of-smart-interface}Detail of the smart 
interface.}
\end{figure}

@@

In the next section we re-examine the model and the Marlowe language, looking at possible extensions, alternative design decisions and ways in which we can formally analyse Marlowe contracts.

@@

That is, for each contract do there exist sequences of inputs and observables such that stepping the contract with them 
leads to \haskellinline{Null}? Furthermore, do all sequences of inputs and observables eventually evolve to 
\haskellinline{Null}? Some relevant points include:
\begin{itemize}
\item For \haskellinline{When}, in principle, we would need to be able to make \haskellinline{interpretObs st obs os} 
true. However, since there is  a timeout to \haskellinline{When} then there is no need to impose this condition, as we 
will progress at timeout if not before.
\item As we have put timeouts on to \haskellinline{CommitCash} and \haskellinline{Pay}, the only construct that may not 
reduce to \haskellinline{Null} eventually is \haskellinline{RedeemCC}. \haskellinline{RedeemCC} will still reduce to 
\haskellinline{Null} if the commitment that it refers to has expired (and it will produce a 
\haskellinline{DuplicateRedeem} action), but it will be quiescent forever if the money is never comitted in the first 
place.
\item Other constructs will reduce to \haskellinline{Null} eventually as long as their continuations also reduce to 
\haskellinline{Null} (as is the case of \haskellinline{Both}).
\end{itemize}
